\documentclass[12pt, letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage{comment}
\usepackage{ragged2e}
 

\title{First document}
\author{Hubert Farnsworth \thanks{funded by the ShareLaTeX team}}
\date{\today}


\begin{document}
 
\begin{titlepage}
\maketitle
\end{titlepage}
 
\begin{abstract}
This is a simple paragraph at the beginning of the 
document. A brief introduction about the main subject.
\end{abstract}
\newpage
 
In this document some extra packages and parameters
were added. There is a encoding package
an a pagesize and fontsize parameters.
 
This line will start a second Paragraph. And I can
 brake\\ the lines \\and continue in a new line.

This documents contains a lot of comments, non of them
will appear here, only this text.
 
This documents contains a lot of comments, non of them
will appear here, only this text.
 
\begin{comment}
This text won't show up in the compiled pdf
this is just a multi-line comment. Useful
to, for instance, comment out slow-rendering
while working on the draft.
\end{comment}


\begin{flushright}
Example 1: The following paragraph (given in quotes) is an 
example of Center Alignment using the center environment. 
\end{flushright}
 

\setlength{\parindent}{10ex}
This is the text in first paragraph. This is the text in first 
paragraph. This is the text in first paragraph. \par
\noindent %The next paragraph is not indented
This is the text in second paragraph. This is the text in second 
paragraph. This is the text in second paragraph.


\justifying
``\LaTeX is a document preparation system and document markup 
language. LaTeX uses the TeX typesetting program for formatting 
its output, and is itself written in the TeX macro language. 
LaTeX is not the name of a particular editing program, but 
refers to the encoding or tagging conventions that are used 
in LaTeX documents".


\end{document}
